%-------------------------
% ATS-Friendly Resume — Bharani KR
% Overleaf compatible (pdflatex)
% Single column, clean, no graphics, no icons
% Optimized for ATS parsing
%-------------------------

\documentclass[a4paper,11pt]{article}

% ─── Packages ───
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.45in, top=0.4in, bottom=0.4in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{qrcode}

% ─── Colors ───
\definecolor{primary}{HTML}{0055FF}
\definecolor{darktext}{HTML}{0f172a}
\definecolor{mutedtext}{HTML}{334155}
\definecolor{rulecolor}{HTML}{cbd5e1}

% ─── Hyperlinks ───
\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=primary,
    pdfauthor={Bharani KR},
    pdftitle={Bharani KR - Resume},
    pdfsubject={IoT \& Cyber Security Engineer},
}

% ─── Page Style ───
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% ─── Section Formatting ───
\titleformat{\section}{
  \color{darktext}\large\bfseries
}{}{0em}{}[\color{rulecolor}\titlerule]
\titlespacing*{\section}{0pt}{6pt}{3pt}

% ─── List Formatting ───
\setlist[itemize]{
  leftmargin=1.5em,
  itemsep=0pt,
  parsep=0pt,
  topsep=1pt,
  label=\textcolor{primary}{\textbullet}
}

% ─── Custom Commands ───
\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\noindent
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{#1} & \textit{\small #2} \\
    \textit{\small #3} & \textit{\small #4}
  \end{tabularx}
  \vspace{-3pt}
}

\newcommand{\projectHeading}[2]{
  \vspace{2pt}\noindent
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{#1} & \textit{\small #2}
  \end{tabularx}
  \vspace{-3pt}
}

\newcommand{\skillRow}[2]{
  \textbf{#1:} #2 \\[2pt]
}

% ─── Document ───
\begin{document}

%─────────────────────────────────
% HEADER
%─────────────────────────────────
\noindent
\begin{minipage}[c]{0.15\textwidth}
  \hphantom{\qrcode[height=0.55in]{https://bharani01.netlify.app}}
\end{minipage}%
\begin{minipage}[c]{0.7\textwidth}
  \centering
  {\LARGE\bfseries BHARANI KR} \\[3pt]
  {\small IoT \& Cyber Security Engineer \enspace$|$\enspace Embedded AI Developer} \\[4pt]
  {\small
    Chennai, India \enspace$|$\enspace
    +91 93637 25862 \enspace$|$\enspace
    \href{mailto:bharani.cyber@gmail.com}{bharani.cyber@gmail.com} \\[2pt]
    \href{https://linkedin.com/in/bharani-k-r-45a950354}{LinkedIn} \enspace$|$\enspace
    \href{https://github.com/bharani-01}{GitHub} \enspace$|$\enspace
    \href{https://bharani01.netlify.app}{Portfolio}
  }
\end{minipage}%
\begin{minipage}[c]{0.15\textwidth}
  \begin{flushright}
    \qrcode[height=0.55in]{https://bharani01.netlify.app}
  \end{flushright}
\end{minipage}

\vspace{-6pt}

%─────────────────────────────────
% SUMMARY
%─────────────────────────────────
\section{Summary}
{\small Hardware-software engineer focused on real-time embedded systems, sensor fusion, and computer vision. Strong foundation in C/C++ and Python with hands-on experience in YOLO-based object detection, IoT firmware development, and full-stack web applications. \textbf{Seeking Summer 2026 Internships in Embedded Systems, AI/ML, or IoT.}}

%─────────────────────────────────
% EDUCATION
%─────────────────────────────────
\section{Education}
\resumeSubheading
  {B.Tech in Cyber Security \& IoT}
  {Expected 2028}
  {Sri Ramachandra Faculty of Engineering and Technology (SRET), Chennai}
  {}

\vspace{-1pt}
{\footnotesize\textbf{Relevant Coursework:} Embedded Systems, Network Security, Data Structures, IoT Protocols, Machine Learning, Computer Vision.}

%─────────────────────────────────
% TECHNICAL SKILLS
%─────────────────────────────────
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}l X@{}}
  \textbf{Languages}        & C, C++, Python, JavaScript, SQL, HTML/CSS \\[2pt]
  \textbf{Hardware \& IoT}  & ESP8266, ESP32, Arduino, Raspberry Pi, I2C/SPI, UART, Sensor Integration \\[2pt]
  \textbf{AI \& Vision}     & YOLOv8/v11, PaddleOCR, OpenCV, Google MediaPipe, TensorFlow Lite \\[2pt]
  \textbf{Web \& Tools}     & React, Next.js, Node.js, Flask, PostgreSQL, MongoDB, Supabase, Prisma, Git \\[2pt]
  \textbf{Platforms}         & Linux, Vercel, Render, QGIS, Arduino IDE, VS Code \\
\end{tabularx}

%─────────────────────────────────
% ENGINEERING PROJECTS
%─────────────────────────────────
\section{Engineering Projects}

\projectHeading
  {TruFleet: Vehicle Authorization Platform \enspace\textnormal{\small\textbar\enspace \textit{React 18, Node.js, Supabase, PostgreSQL RLS}}}
  {VIT TetherX 2026}
\begin{itemize}
  \item \textbf{Use Case:} SaaS platform for commercial vehicle identity management, insurance verification, and automated fleet scheduling.
  \item \textbf{2nd Place (National Hackathon):} Built a 5-step compliance chain and implemented Supabase RLS for multi-org data isolation. 
\end{itemize}

\projectHeading
  {TITAN-V2 Autonomous Rover \enspace\textnormal{\small\textbar\enspace \textit{C++, ESP32, ESP8266, ESP-CAM, WebSockets, I2C}}}
  {2025}
\begin{itemize}
  \item \textbf{Use Case:} Autonomous exploration rover featuring real-time video streaming and a 6-axis robotic arm for remote payload manipulation.
  \item Engineered a multi-MCU architecture with 6 ultrasonic sensors and MPU-6050 IMU, utilizing WebSockets for low-latency telemetry streaming.
\end{itemize}

\projectHeading
  {RoadCams: Campus AI Surveillance \enspace\textnormal{\small\textbar\enspace \textit{Python, YOLOv11, PaddleOCR, PostgreSQL, QGIS}}}
  {2024}
\begin{itemize}
  \item \textbf{Use Case:} Campus-wide vehicle tracking system to detect unauthorized entries, alert security, and map vehicle trajectories.
  \item Trained YOLOv11 models for 95\%+ ANPR accuracy; implemented duplicate detection, blacklist alerts, and spatial visualization on QGIS.
\end{itemize}

\projectHeading
  {AttendPro: Anti-Proxy Attendance \enspace\textnormal{\small\textbar\enspace \textit{Flutter, Node.js, MongoDB, HTML/CSS/JS}}}
  {2025}
\begin{itemize}
  \item \textbf{Use Case:} Cross-platform educational tool designed to eliminate proxy attendance fraud and automate faculty reporting workflows.
  \item Enforced attendance integrity via device fingerprinting and geo-fencing; built a REST API capable of handling 500+ concurrent users.
\end{itemize}

\projectHeading
  {Inventory Management \enspace\textnormal{\small\textbar\enspace \textit{Next.js, PostgreSQL, Prisma, Node.js}}}
  {2025}
\begin{itemize}
  \item \textbf{Use Case:} Omnichannel retail solution unifying physical counter billing with a live-synced e-commerce storefront.
  \item Implemented real-time stock deductions, IP-based audit logging for security, rate limiting, and scheduled email report generation.
\end{itemize}

\end{document}
